### 2010-02-15 doc/manuals/janitor/tex_installation/installation.tex
Smallish series of updates on Janitor documentation.

If you are using regular Debian or Ubuntu packages, then the Janitor
can be installed as root by "apt-get install nordugrid-arc1-janitor".
Installing it will not drag other components of ARC with it since the
Janitor can be used in its own right or in conjunction with another
grid system, possibly. Packages for Redhat/Fedora and SuSE/OpenSuSE are
also provided, the redland library however may not yet be available for
those systems.

@@

Furthermore it is recommended to install the ontology editor 
Prot\`eg\`e\footnote{\href{http://protege.stanford.edu}{http://protege.stanford.edu}}
in order to be to easily maintain the knowledge database of installable
packages.  At the time of writing, no Linux distribution is offering
packages for this fine tool. The basic editing can also be performed
fairly easily without that tool, but one is unlikely to use the technology
to its full potential, then.

>>>>

If you are using regular Debian or Ubuntu packages, then the Janitor
can be installed as root by "apt-get install nordugrid-arc1-janitor".
Installing it will not drag other components of ARC with it, since the
Janitor can be used in its own right -- or in conjunction with another
grid system, possibly. Packages for Redhat/Fedora and SuSE/OpenSuSE are
also provided, the redland library however may not yet be available for
those systems.

@@

Furthermore many users will want to consider installing the ontology editor 
Prot\`eg\`e\footnote{\href{http://protege.stanford.edu}{http://protege.stanford.edu}}
to easily maintain the knowledge database of installable
packages.  At the time of writing, no Linux distribution is offering
packages for this fine tool. However, the basic editing can also be
performed fairly easily without that tool, and everyone is working on
simplifying that process.
